---
title: "glmers for reversal"
author: "Sophie Paolizzi"
date: "4/4/2022"
output: html_document
---

```{r setup, include=FALSE}
pacman::p_load(tidyverse, dplyr, sjPlot, readr, janitor, ggplot2,wesanderson, cowplot, flextable, plotly, emmeans, lme4, qualtRics, sjPlot, circular, pracma, cowplot, psych, lattice)
##### Load Data and setwd
ll = FALSE
if (ll == TRUE) {
  home_directory <- "/proj/mnhallqlab/users/sophie/ReversalTask/"
  data_dir <- file.path(paste0(home_directory, "data/"))
} else {
  home_directory <- "~/github_repos/ReversalTask/"
  data_dir <- file.path(paste0(home_directory, "Data/"))
}
load(file = paste0(data_dir,'base_effects_data.RData'))

data <- df %>% dplyr::filter(rt !=0) %>% dplyr::filter(!isResponseCorrect == 0) %>% filter(subject != 270470)

data$rt_log <- log(data$rt)
data$rt_inv<- -1/1000*(data$rt)
minfo<- list()
load("~/github_repos/Cannon_Task/Analysis/lmer/glmer_mods.Rdata")
data$ResponseCorrect_num <- data$ResponseCorrect_num %>% dplyr::recode("-1" = 0, "1" = 1)
data$trial_z <- scale(data$trial_number)
data$total_trial_z <- scale(data$total_trialnum)
data$prevRT_log <- lag(log(data$rt))
```


### Base model
Start with the basics.... should be an effect of trial number based on tidy_markdown. 
```{r}
minfo[["mod0"]] <- c(fixed="Intercept", l2="Intercept/Subject")
mod0 <- glmer(ResponseCorrect_num ~ 1 + (1|subject), family = binomial, control = glmerControl(optimizer = "bobyqa"),
    nAGQ = 10, data = df)
plot(fitted(mod0), residuals(mod0))

minfo[["mod1"]] <- c(fixed="Total Trial", l2="Intercept/Subject")
mod1 <- glmer(ResponseCorrect_num ~  total_trialnum + (1|subject), data = df, family = binomial, control = glmerControl(optimizer = "bobyqa"),
    nAGQ = 10)
#note: trial_number is within-block (i.e., 1-40)
minfo[["mod1.1"]] <- c(fixed="block_trial_number, block number", l2="Intercept/Subject")
mod1.1 <- glmer(ResponseCorrect_num ~  trial_number + block_number + (1|subject), data = df, family = binomial, control = glmerControl(optimizer = "bobyqa"),
    nAGQ = 10); summary(mod1.1)
resids <- residuals(mod1.1)
fitted <- fitted(mod1.1)
plot(fitted, resids)
AIC(mod0, mod1, mod1.1)
```

### Rescale trials
Carry 2.1 forward, total_trial covers what we need best. Z-scoring within subject as well. 
```{r}
minfo[["mod2"]] <- c(fixed="block_trial_z, block number", l2="Intercept/Subject")
mod2 <- glmer(ResponseCorrect_num ~ trial_z + block_number + (1 |subject), data = df, family = binomial, control = glmerControl(optimizer = "bobyqa"),
    nAGQ = 10); summary(mod2)

minfo[["mod2.1"]] <- c(fixed="total_trial_z", l2="Intercept/Subject")
mod2.1 <- glmer(ResponseCorrect_num ~ total_trial_z + (1 |subject), data = df, family = binomial, control = glmerControl(optimizer = "bobyqa"),
    nAGQ = 10)

AIC(mod2,mod2.1)
```


### Add in RT
seems trial-wise RT is doing a little, but not much. 
```{r}
minfo[["mod3"]] <- c(fixed="total_trial_z, PrevRT", l2="Intercept/Subject")
mod3 <- glmer(ResponseCorrect_num ~ total_trial_z + rt_log + (1 |subject), data = df, family = binomial, control = glmerControl(optimizer = "bobyqa"))
AIC(mod2.1, mod3)
```


### Add in previous RT
We've got an effect here of previous RT; seems to be a relatively clear winner, 
```{r}
minfo[["mod3.1"]] <- c(fixed="total_trial_z, PrevRT, RT", l2="Intercept/Subject")
mod3.1 <- glmer(ResponseCorrect_num ~ total_trial_z + prevRT_log + rt_log + (1 |subject), data = df, family = binomial, control = glmerControl(optimizer = "bobyqa"))
summary(mod3.1)
car::vif(mod3.1)
dependlab::render_flex_aictab(minfo=minfo, mod0, mod1, mod1.1, mod2, mod2.1, mod3, mod3.1) %>% autofit() 
```


### Task_phase
Some clear improvement! Good news for our hypotheses re: task phase shifts
```{r}
minfo[["mod4"]] <- c(fixed="total_trial_z, PrevRT, task phase", l2="Intercept/Subject")
mod4 <- glmer(ResponseCorrect_num ~ total_trial_z + prevRT_log + rt_log + task_phase + (1 |subject), data = df, family = binomial, control = glmerControl(optimizer = "bobyqa"))
summary(mod4)
dependlab::render_flex_aictab(minfo=minfo, mod0, mod1, mod1.1, mod2, mod2.1, mod3, mod3.1, mod4) %>% autofit() 
```

### previous feedback (previous error, kind of)
A previous perceived error leads to choosing the wrong stimulus on the current trial. Seems like a basic win-stay lose-switch strategy, but ignoring the probabilistic part. 
```{r}
minfo[["mod5"]] <- c(fixed="total_trial_z, PrevRT, task phase, previous feedback", l2="Intercept/Subject")
mod5 <- glmer(ResponseCorrect_num ~ total_trial_z + prevRT_log + rt_log + task_phase + prevFeedback + (1 |subject), data = df, family = binomial, control = glmerControl(optimizer = "bobyqa"))
summary(mod5)
dependlab::render_flex_aictab(minfo=minfo, mod0, mod1, mod1.1, mod2, mod2.1, mod3, mod4, mod5) %>% autofit() 
```

### previous response (sort of a stickiness type deal?)
Clear winner in 6.1; Interaction between feedback and response; starting to see some upward trends in collinearity we should watch out for. 
```{r}
minfo[["mod6"]] <- c(fixed="tot_trial_z, PrevRT, RT, phase, prevFeed, prevResp", l2="Intercept/Subject")
mod6 <- glmer(ResponseCorrect_num ~ total_trial_z + prevRT_log + rt_log + task_phase + prevFeedback + prevResponse + (1 |subject), data = df, family = binomial, control = glmerControl(optimizer = "bobyqa"))

minfo[["mod6.1"]] <- c(fixed="tot_trial_z, PrevRT, RT, phase, prevFeed*prevResp", l2="Intercept/Subject")
mod6.1 <- glmer(ResponseCorrect_num ~ total_trial_z + prevRT_log + rt_log + task_phase + prevFeedback*prevResponse + (1 |subject), data = df, family = binomial, control = glmerControl(optimizer = "bobyqa"))
AIC(mod5, mod6, mod6.1)
car::vif(mod6.1)
summary(mod6.1)
```

### Interaction extensions and experimentation
We see some potential here for a phasexfeedback interaction, suggesting that previous feedback in the reversal block is slightly less salient. Also seems clear we shouldn't hope for a 3-way interaction with task phase,previous feedback, and previous response, collinearity is intense.  A phase x previous response interaction also seems to slightly improve the model fit - will be interesting to see how that shakes out in the random efffects structure.
```{r}
minfo <- list()
minfo[["mod6.2"]] <- c(fixed="tot_trial_z, PrevRT, RT, phase*prevFeed, prevResp", l2="Intercept/Subject")
mod6.2 <- glmer(ResponseCorrect_num ~ total_trial_z + prevRT_log + rt_log  + task_phase + task_phase*prevFeedback + prevResponse + (1 |subject), data = df, family = binomial, control = glmerControl(optimizer = "bobyqa"))

minfo[["mod6.3"]] <- c(fixed="tot_trial_z, PrevRT, RT, phase*prevResp + prevFeed", l2="Intercept/Subject")
mod6.3 <- glmer(ResponseCorrect_num ~ total_trial_z + prevRT_log + rt_log + task_phase + task_phase*prevResponse + prevFeedback + (1 |subject), data = df, family = binomial, control = glmerControl(optimizer = "bobyqa"))

minfo[["mod6.4"]] <- c(fixed="tot_trial_z, PrevRT, RT, phase, phase*prevFeed, prevFeed*prevResp", l2="Intercept/Subject")
mod6.4 <- glmer(ResponseCorrect_num ~ total_trial_z + prevRT_log + rt_log + task_phase + prevFeedback*task_phase + prevFeedback*prevResponse + (1 |subject), data = df, family = binomial, control = glmerControl(optimizer = "bobyqa"))
summary(mod6.4)

minfo[["mod6.5"]] <- c(fixed="tot_trial_z, PrevRT, RT, phase*prevFeed*prevResp", l2="Intercept/Subject")
mod6.5 <- glmer(ResponseCorrect_num ~ total_trial_z + rt_log + prevRT_log + task_phase + task_phase*prevFeedback*prevResponse + (1 |subject), data = df, family = binomial, control = glmerControl(optimizer = "bobyqa")) #very collinear, probably not salvageable
car::vif(mod6.5)

#dropping out rt_log since we aren't seeing much there. Also see if dropping out 3-way helps singularity
minfo[["mod6.6"]] <- c(fixed="tot_trial_z, PrevRT, phase, phase*prevFeed, prevFeed*prevResp", l2="Intercept/Subject")
mod6.6 <- glmer(ResponseCorrect_num ~ total_trial_z + prevRT_log + task_phase*prevResponse + prevFeedback*task_phase + prevFeedback*prevResponse + (1 |subject), data = df, family = binomial, control = glmerControl(optimizer = "bobyqa"))

summary(mod6.6)

dependlab::render_flex_aictab(minfo=minfo, mod0, mod1, mod1.1, mod2, mod2.1, mod3, mod4, mod5, mod6, mod6.1, mod6.2, mod6.3, mod6.4, mod6.5, mod6.6) %>% autofit() 
plot_model(mod6.6, type = "pred", terms = c("prevFeedback", "prevResponse"))
```



##responseandfeedbackcategory variable....
Not working, and I don'tknow of a dummy code that lets me do a 4-way contrast... stick with 6 for now
```{r}
minfo[["mod7"]] <- c(fixed="tot_trial_z, PrevRT, phase, phase*prevFeed, prevFeed*prevResp", l2="Intercept/Subject")
mod7 <- glmer(ResponseCorrect_num ~ total_trial_z + prevRT_log + responseAndFeedbackCategory*task_phase + responseAndFeedbackCategory + (1 |subject), data = df, family = binomial, control = glmerControl(optimizer = "bobyqa"))
```

