---
title: "Reversal StaySwitch Models; Fixed Effects"
author: "Sophie Paolizzi"
date: '2022-06-13'
output: html_document
---

#### Michael Feedback 6.08.22
1. Have you coded a variable for trial number since reversal? I would probably code this, and -100/this to capture how accuracy scales with trials since the reversal happened.That’s close to your stated hypothesis about sensitivity to reversal.
- Done, added reversal sensitivity variable. I also scaled it as the difference in scales was causing convergence issues; curious if that has conceptual problems. 

2. Is previous response the identity of the previous response (like L/R or some other factor) or is it whether the previous response was correct (basically a lagged copy of the DV)?
If it’s the lagged copy, then this is capturing good behavior (choosing good things), but may not capture a preference for a given stimulus (that has a certain identity). Is that how you’re thinking about it?

- this is in fact the accuracy of the previous stim. I added a stim_choice that captures the stim identity element, and lagged that as well so we can test both.

3.I am thinking that the current setup of the models is probably capturing a lot of the key variance, but in ways that are hard to interpret and lead to challenges in the ranef corrs. I would consider running models that use stimulus identity as the DV or maybe even use stay/switch as 1/0. Could you send me your data.frame? I could probably prototype a couple of things for comparison, even if ultimately my hunch proves not to be useful.
 
I’m generally thinking of models that are closer to:
glmer(stim_choice ~ prior_A * prior_reward * task_phase + (1 | subject))

If you wanted to stay with accuracy coding, I think it would be:
glmer(choose_best ~ switch * prior_reward  * task_phase + (1|subject))

Finally, we’ve approached these kinds of analyses before in terms of stay/switch as outcome (as mentioned above). I think this would be:
glmer(stay ~ prior_stay * prior_reward * task_phase * stationary_trial + (1|subject))

Will run each of these to see how the story changes in each set. Beginning with stim_choice, and will sub in the other DVs for the final-ish model. 

4. With the trial regressor, it’s more like
glmer(choose_best ~ switch * prior_reward  * task_phase * stationary_trial + (1|subject))

where that stationary trial is the trial number since either beginning of block (acquisition) or post-reversal

 - recoded the "stationary trial" as phase_trialnum, and scaled within phase due to convergence issues. 

6. To your specific questions, I think the 3-way interaction reflects that previous choice outcome, not identity is in the interaction, so you get a lot of collinearity when people make repeated, good choices. And that probably spills over into the ranef structure, which is too correlated to be entirely trustworthy.

Great, thanks for resolving. Makes sense to me. 

### Markdown Purpose and Content

This markdown follows the model selection procedure for the reversal task from the base model through the random effects structure. 

### Variables at Play
**ResponseCorrect_num**. Outcome variable: whether participants selected the outcome with a higher  (70%) probabilistic chanCe of reward.

**prevrt_log**. Reaction time in previous trial. 

**rt_log**. Reaction time of current trial. 

**block_number**. block number (1-5) of the task. 

**trial**. Within-phase trial number.

**since_reversal **. Number of trials since a reversal has occurred. Also resets at the beginning of the phase, so counts beginning of block  as a "reversal". 

**task_phase**. Reversal vs. Acquisition.

**prev_choice**. The response participants selected on the previous trial (Acq_stim or Rev_stim). 

**prevFeedback**. Feedback received from the previous trial - importantly, this is probabilistic."Correct" feedback means participants were told they were correct, where "incorrect" feedback means participants were told they were incorrect. 

**ResponseandFeedbackCategory**. There are 4 possible outcomes combining previous response and previous feedback on any given trial. A participant could respond correctly and receive congruent feedback (CRCF; correct resp, feedback = "correct"); they could respond incorrectly and receieve congruent feedback (IRCF; incorrect resp, feedback = "correct"); they could respond correctly and recieve incongruent feedback (CRIF; correct resp, feedback = "incorrect"); or they could respond incorrectly and recieve incorrect feedback (IRIF; incorrect resp, feedback = "correct"). 

### Hypotheses 
As a reminder, here are the hypotheses at play:

A. In a serial reversal task, there will be a relationship between heightened BPD symptoms (as indexed by the PAI-BOR) and relatively faster detection of contingency reversals, as indicated by fewer incorrect responses post-reversal. These learners will also be less likely to choose the same option consistently across the blocks. 
B.  In a serial reversal task, higher scores on the PSWQ will be associated with relatively slower detection of reversing reward contingencies; Participants with higher PSWQ scores will tend to be consistent in their choices and experience more errors (and less correct answers) in learning post-reversal. 

```{r setup, include=FALSE}
pacman::p_load(tidyverse, dplyr, sjPlot, readr, janitor, ggplot2,wesanderson, cowplot, flextable, plotly, emmeans, lme4, qualtRics, sjPlot, circular, pracma, cowplot, psych, lattice)
##### Load Data and setwd
ll = FALSE
if (ll == TRUE) {
  home_directory <- "/proj/mnhallqlab/users/sophie/ReversalTask/"
  data_dir <- file.path(paste0(home_directory, "data/"))
} else {
  home_directory <- "~/github_repos/ReversalTask/"
  data_dir <- file.path(paste0(home_directory, "Data/"))
}
load(file = paste0(data_dir,'base_effects_data.RData'))

data <- df %>% dplyr::filter(rt !=0) %>% dplyr::filter(!isResponseCorrect == 0) %>% filter(subject != 270470)

data$rt_log <- log(data$rt)
data$rt_inv<- -1/1000*(data$rt)
minfo<- list()
load("~/github_repos/Cannon_Task/Analysis/lmer/glmer_mods.Rdata")

data <- data %>% 
  mutate(trial_z = scale(trial_number),
         total_trial_z = scale(total_trialnum),
         task_phase = as.factor(task_phase),
         prevFeedback = as.factor(prevFeedback),
         phase_trialnum_z = scale(phase_trialnum),
         since_reversal = scale(-100/phase_trialnum),
         ResponseCorrect_num = dplyr::recode(ResponseCorrect_num, "-1" = 0, "1" = 1)) %>% 
  group_by(subject) %>% mutate(prevResponse = as.factor(lag(Response)),
                               prevrt_log = lag(rt_log)) %>% ungroup()


#stim_ident
data$stim_choice <- ifelse(data$task_phase == "Acquisiton" & data$ResponseCorrect == 1, "Acq_stim", "tmp")
data$stim_choice <- ifelse(data$task_phase == "Reversal" & data$ResponseCorrect == 1, "Rev_stim", data$stim_choice)
data$stim_choice <- ifelse(data$task_phase == "Reversal" & data$ResponseCorrect == 0, "Acq_stim", data$stim_choice)
data$stim_choice <- ifelse(data$task_phase == "Acquisiton" & data$ResponseCorrect == 0, "Rev_stim", data$stim_choice)
data$stim_choice <- as.factor(data$stim_choice)
data$stim_choice <- relevel(data$stim_choice, ref = "Acq_stim")
data$stim_choice_num <- as.numeric(recode(data$stim_choice, 'Acq_stim' = 0, 'Rev_stim' = 1))
data$prev_choice <- lag(data$stim_choice)
#random shorter things
data$prev_choice <- lag(data$stim_choice)
data$prev_choice <- lag(data$stim_choice)
data$phase_early <- ifelse(data$phase_trialnum_z <0, "early", "late")
data$StaySwitch <- as.factor(ifelse(data$stim_choice != data$prev_choice, "Switch", "Stay"))
data$StaySwitch_lag <-lag(data$StaySwitch)
```

### Standard trial-level covariates; Trial
According to Michael's edits and beginning analysis from a stimulus_choice perspective; starting with trial; I compared total_trial_z, or trial number across the full task and all blocks, trial_z which is the scaled, within-block trial number, and the within-phase scaled trial number. I realized trial_z is inherently going to have problems with collinearity once task_phase gets introduced, so going with phase_trialnum_z as Michael originally suggested. 
```{r}
mod0 <- glmer(StaySwitch ~ trial_z + (1 | subject), family = binomial, control = glmerControl(optimizer = "bobyqa"), nAGQ = 10, data = data)

mod0.1 <- glmer(StaySwitch ~ total_trial_z + (1 | subject), family = binomial, control = glmerControl(optimizer = "bobyqa"), nAGQ = 10, data = data)

mod0.2 <- glmer(StaySwitch ~ phase_trialnum_z + (1 | subject), family = binomial, control = glmerControl(optimizer = "bobyqa"), nAGQ = 10, data = data)


resids <- residuals(mod0)
fitted <- fitted(mod0)
plot(fitted, resids)
AIC(mod0, mod0.1, mod0.2)
summary(mod0)
```

```{r}
mod1 <- glmer(StaySwitch ~ phase_trialnum_z + rt_log + (1 | subject), family = binomial, control = glmerControl(optimizer = "bobyqa"), nAGQ = 10, data = data)
summary(mod1)

mod1.1 <- glmer(StaySwitch ~ phase_trialnum_z + rt_log + prevrt_log + (1 | subject), family = binomial, control = glmerControl(optimizer = "bobyqa"),
                nAGQ = 10, data = data)
summary(mod1.1)
AIC(mod0, mod1, mod1.1)
car::vif(mod1.1)
```



```{r}
mod2 <- glmer(StaySwitch ~ phase_trialnum_z + rt_log + prevrt_log + task_phase + (1 | subject), family = binomial, control = glmerControl(optimizer = "bobyqa"),
                nAGQ = 1, data = data)

summary(mod2)

AIC(mod1.1, mod2)
```

check out previous feedback; expect it to be huge
```{r}


mod3 <- glmer(StaySwitch ~ phase_trialnum_z + rt_log + prevrt_log + task_phase + prevFeedback + (1 | subject), family = binomial, control = glmerControl(optimizer = "bobyqa"),
                nAGQ = 1, data = data)

summary(mod3)

AIC(mod3, mod2)
```

task phase effect seems clear now
```{r}
mod4 <- glmer(StaySwitch ~ phase_trialnum_z + rt_log + prevrt_log + task_phase + prevFeedback + prev_choice + (1 | subject), family = binomial, control = glmerControl(optimizer = "bobyqa"), nAGQ = 1, data = data)

AIC(mod3, mod4)
summary(mod4)
car::vif(mod4)
```

```{r}

mod5 <- glmer(StaySwitch ~ phase_trialnum_z + rt_log + prevrt_log + task_phase + prevFeedback + since_reversal + prev_choice + (1 | subject), family = binomial, control = glmerControl(optimizer = "bobyqa"), nAGQ = 1, data = data)

mod5.1 <- glmer(StaySwitch ~ phase_trialnum_z + rt_log + prevrt_log + task_phase + prevFeedback + StaySwitch_lag + since_reversal + (1 | subject), family = binomial, control = glmerControl(optimizer = "bobyqa"), nAGQ = 1, data = data)

mod5.2 <- glmer(StaySwitch ~ phase_trialnum_z + rt_log + prevrt_log + task_phase + prevFeedback + prev_choice + StaySwitch_lag + since_reversal + (1 | subject), family = binomial, control = glmerControl(optimizer = "bobyqa"), nAGQ = 1, data = data)

mod5.3 <- glmer(StaySwitch ~ rt_log + prevrt_log + task_phase + prevFeedback + prev_choice + StaySwitch_lag + since_reversal + (1 | subject), family = binomial, control = glmerControl(optimizer = "bobyqa"), nAGQ = 1, data = data)

AIC(mod5.1, mod5, mod5.2, mod5.3, mod6, mod6.1, mod6.2)
car::Anova(mod6.2, type = 3)
car::vif(mod5.3)
```



```{r}
mod6 <- glmer(StaySwitch ~  rt_log + prevrt_log + task_phase + prev_choice + prevFeedback*StaySwitch_lag + since_reversal + (1 | subject), family = binomial, control = glmerControl(optimizer = "bobyqa"), nAGQ = 1, data = data)

mod6.1 <- glmer(StaySwitch ~ rt_log + prevrt_log + task_phase*since_reversal +prev_choice + prevFeedback*StaySwitch_lag + since_reversal + (1 | subject), family = binomial, control = glmerControl(optimizer = "bobyqa"), nAGQ = 1, data = data)

mod6.2 <- glmer(StaySwitch ~ rt_log + prevrt_log + task_phase*since_reversal + prevFeedback*StaySwitch_lag  + (1 | subject), family = binomial, control = glmerControl(optimizer = "bobyqa"), nAGQ = 1, data = data)
car::Anova(mod6.3, type = 3)
car::vif(mod6.2)


mod6.3 <- glmer(StaySwitch ~ rt_log + prevrt_log + task_phase*since_reversal + task_phase*prev_choice + prevFeedback*StaySwitch_lag +  (1 | subject), family = binomial, control = glmerControl(optimizer = "bobyqa"), nAGQ = 1, data = data)

mod6.4 <- glmer(StaySwitch ~ rt_log + prevrt_log + prev_choice + task_phase*since_reversal*prevFeedback*StaySwitch_lag + (1 | subject), family = binomial, control = glmerControl(optimizer = "bobyqa"), nAGQ = 1, data = data)

mod6.4 <- glmer(StaySwitch ~ rt_log + prevrt_log + prev_choice + task_phase*since_reversal*prevFeedback + prevFeedback*StaySwitch_lag + (1 | subject), family = binomial, control = glmerControl(optimizer = "bobyqa"), nAGQ = 1, data = data)

AIC(mod6.3, mod6.2, mod6.1, mod6, mod6.4)
car::Anova(mod6.4, type = 3)
car::vif(mod6.4)
```

```{r}
mod7 <- glmer(StaySwitch ~ rt_log + prevrt_log + task_phase*since_reversal + task_phase*prev_choice + prevFeedback*StaySwitch_lag + (1+ prevFeedback| subject), family = binomial, control = glmerControl(optimizer = "bobyqa"), nAGQ = 1, data = data)
AIC(mod6.3, mod7)
car::vif(mod7)
car::Anova(mod7, type = 3)

mod7.1 <- glmer(StaySwitch ~ rt_log + prevrt_log + task_phase*since_reversal + task_phase*prev_choice + prevFeedback*StaySwitch_lag + (1 + prevFeedback + prevrt_log | subject), family = binomial, control = glmerControl(optimizer = "bobyqa"), nAGQ = 1, data = data)
AIC(mod7.1, mod7)
car::vif(mod7.1)
summary(mod7.1)

mod7.2 <- glmer(StaySwitch ~ rt_log + prevrt_log + task_phase*since_reversal*prevFeedback + prevFeedback*StaySwitch_lag  + (1 + prevFeedback + task_phase | subject), family = binomial, control = glmerControl(optimizer = "bobyqa"), nAGQ = 1, data = data)

mod7.3 <- glmer(StaySwitch ~ rt_log + prevrt_log + task_phase*since_reversal*prevFeedback + prevFeedback*StaySwitch_lag + phase_trialnum_z + (1 + prevFeedback + phase_trialnum_z + prevrt_log | subject) + (1 | subject:task_phase), family = binomial, control = glmerControl(optimizer = "bobyqa"), nAGQ = 1, data = data)

AIC(mod6.3, mod7, mod7.1, mod7.2)
car::vif(mod7.1)
summary(mod7.2)
```


```{r}
minfo[["mod0"]] <- c(fixed="within-block trial number", l2="Intercept/Subject", ixns = 'None', max_vif = 'None')
minfo[["mod0.1"]] <- c(fixed="Total trial number", l2="Intercept/Subject", ixns = 'None', max_vif = 'None')
minfo[["mod0.2"]] <- c(fixed="Phase-level Trial", l2="Intercept/Subject", ixns = 'None', max_vif = 'None')
minfo[["mod1"]] <- c(fixed="Trial, RT", l2="Intercept/Subject", ixns = 'None', max_vif = as.character(max(c(car::vif(mod1)))))
minfo[["mod1.1"]] <- c(fixed="Trial, RT, prevRT", l2="Intercept/Subject", ixns = 'None', max_vif =as.character(max(c(car::vif(mod1.1)))))
minfo[["mod2"]] <- c(fixed="Trial, RT, prevRT, task_phase", l2="Intercept/Subject", ixns = 'None', max_vif =as.character(max(c(car::vif(mod2)))))
minfo[["mod3"]] <- c(fixed="Trial, RT, prevRT, task_phase, previous feedback", l2="Intercept/Subject", ixns = 'None', max_vif =as.character(max(c(car::vif(mod3)))))
minfo[["mod4"]] <- c(fixed="Trial, RT, prevRT, task_phase, previous feedback, previous choice", l2="Intercept/Subject", ixns = 'None', max_vif =as.character(max(c(car::vif(mod3)))))
minfo[["mod5"]] <- c(fixed="Trial, RT, prevRT, task_phase, previous feedback, previous choice, time since reversal", l2="Intercept/Subject", ixns = 'None', max_vif =as.character(max(c(car::vif(mod5)))))
minfo[["mod5.1"]] <- c(fixed="Trial, RT, prevRT, task_phase, previous feedback, time since reversal, lagged stay switch", l2="Intercept/Subject", ixns = 'None', max_vif =as.character(max(c(car::vif(mod5.1)))))
minfo[["mod5.2"]] <- c(fixed="Trial, RT, prevRT, task_phase, previous feedback, time since reversal, lagged stay switch", l2="Intercept/Subject", ixns = 'None', max_vif =as.character(max(c(car::vif(mod5.2)))))
minfo[["mod5.3"]] <- c(fixed="RT, prevRT, task_phase, previous feedback, time since reversal, lagged stay switch, previous choice", l2="Intercept/Subject", ixns = 'None', max_vif =as.character(max(c(car::vif(mod5.3)))))
minfo[["mod6"]] <- c(fixed="RT, prevRT, task_phase, previous feedback x lagged stay switch, time since reversal, previous choice", l2="Intercept/Subject", ixns = 'None', max_vif =as.character(max(c(car::vif(mod6)))))
minfo[["mod6.1"]] <- c(fixed="RT, prevRT, previous choice", l2="Intercept/Subject", ixns = ' time since reversal x task phase, previous feedback x lagged stay switch ', max_vif =as.character(max(c(car::vif(mod6.1)))))
minfo[["mod6.2"]] <- c(fixed="RT, prevRT", l2="Intercept/Subject", ixns = ' time since reversal x task phase, previous feedback x lagged stay switch ', max_vif =as.character(max(c(car::vif(mod6.2)))))
minfo[["mod6.3"]] <- c(fixed="RT, prevRT", l2="Intercept/Subject", ixns = ' time since reversal x task phase, previous feedback x lagged stay switch, task phase x previous choice ', max_vif =as.character(max(c(car::vif(mod6.3)))))
minfo[["mod6.4"]] <- c(fixed="RT, prevRT", l2="Intercept/Subject", ixns = ' time since reversal x task phase x previous feedback x lagged stay switch ', max_vif =as.character(max(c(car::vif(mod6.4)))))
minfo[["mod7"]] <- c(fixed="RT, prevRT", l2="Intercept, previous Feedback /Subject", ixns = ' time since reversal x task phase, task phase x previous choice,  x previous feedback x lagged stay switch ', max_vif =as.character(max(c(car::vif(mod7)))))
minfo[["mod7.1"]] <- c(fixed="RT, prevRT", l2="Intercept, previous feedback, previous RT/Subject", ixns = ' time since reversal x task phase, task phase x previous choice,  x previous feedback x lagged stay switch ', max_vif =as.character(max(c(car::vif(mod7.1)))))
minfo[["mod7.2"]] <- c(fixed="RT, prevRT", l2="Intercept, previous feedback, task phase/Subject", ixns = ' time since reversal x task phase, task phase x previous choice,  x previous feedback x lagged stay switch ', max_vif =as.character(max(c(car::vif(mod7.2)))))
minfo[["mod7.3"]] <- c(fixed="RT, prevRT, phase_trialnum_z", l2="Intercept, previous feedback, phase_trialnum_z, previous RT /Subject", ixns = ' time since reversal x task phase, task phase x previous choice,  x previous feedback x lagged stay switch ', max_vif =as.character(max(c(car::vif(mod7.3)))))

minfo[["stay_switch"]] <- c(fixed="RT, prevRT", l2="previous feedback, previous RT /Subject", ixns = ' time since reversal x task phase, task phase x previous choice,  x previous feedback x lagged stay switch ', max_vif =as.character(max(c(car::vif(stay_switch)))))

mlist <- list()
mlist[["mod0"]] <- mod0
mlist[["mod0.1"]] <- mod0.1
mlist[["mod0.22"]] <- mod0.2
mlist[["mod1"]] <- mod1
mlist[["mod1.1"]] <- mod1.1
mlist[["mod2"]] <- mod2
mlist[["mod3"]] <- mod3
mlist[["mod4"]] <- mod4
mlist[["mod5"]] <- mod5
mlist[["mod5.1"]] <- mod5.1
mlist[["mod5.2"]] <- mod5.2
mlist[["mod5.3"]] <- mod5.3
mlist[["mod6"]] <- mod6
mlist[["mod6.1"]] <- mod6.1
mlist[["mod6.2"]] <- mod6.2
mlist[["mod6.3"]] <- mod6.3
mlist[["mod6.4"]] <- mod6.4
mlist[["mod7"]] <- mod7
mlist[["mod7.1"]] <- mod7.1
mlist[["mod7.2"]] <- mod7.2
mlist[["mod7.3"]] <- mod7.3
mlist[["stay_switch"]] <- stay_switch

table_stay_switch <- dependlab::render_flex_aictab(minfo = minfo, mlist = mlist) %>% autofit()
summary(mod7)
```

