---
title: "Base_LMERs"
author: "Sophie Paolizzi"
date: "2/21/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#load up
pacman::p_load(tidyverse, sjPlot, readr, janitor, ggplot2,wesanderson, cowplot, flextable, plotly, emmeans, lme4, qualtRics, sjPlot, circular, pracma, cowplot, psych, lattice)
##### Load Data and setwd
ll = FALSE
if (ll == TRUE) {
  home_directory <- "/proj/mnhallqlab/users/sophie/ReversalTask/"
  data_dir <- file.path(paste0(home_directory, "data/"))
} else {
  home_directory <- "~/github_repos/ReversalTask/"
  data_dir <- file.path(paste0(home_directory, "Data/"))
}
load(file = paste0(data_dir,'base_effects_data.RData'))
data = "only_zeros" #only_zeros
  
if (data == "only_zeros"){
  data <- df %>% filter(rt !=0) %>% filter(!isResponseCorrect == 0)
  #only cuts out rts that are actually 0 (meaning people were pressing at exactly 50ms): about 394 trials. This leaves things weird-looking
} else if(data == "over_150ms")  {
  data <- within_effects %>% filter(rt >= 150) %>% filter(!isResponseCorrect == 0) # cuts out rts that are less than 150 (meaning people were pressing at 100ms of the stimuli being presented; These data looked the most normal) - this keeps 91% of the data in (cutting only another 400 trials or so): I don;'t want to totally lose peoplew ho are sticky, so I want to cut as little as possible
}
data$rt_log <- log(data$rt)
data$rt_inv<- -1/1000*(data$rt)
hist(data$rt)
hist(data$rt_inv)
hist(data$rt_log)
range(data$rt)
minfo<- list()
```

```{r}
plot(data$isResponseCorrect)
data$trial_z <- scale(data$trial_number)
data$total_trial_z <- scale(data$total_trialnum)
data$prevRT_log <- lag(log(data$rt))
```

### Base model
Start with the basics.... should be an effect of trial number based on tidy_markdown. 
```{r}
minfo[["mod0"]] <- c(fixed="Intercept", l2="Intercept/Subject")
mod0 <- lmer(rt_log ~ 1 + (1|subject), data = data)
plot(fitted(mod0), residuals(mod0))

minfo[["mod1"]] <- c(fixed="Total Trial", l2="Intercept/Subject")
mod1 <- lmer(rt_log ~  total_trialnum + (1|subject), data = data); summary(mod1)
resids <- residuals(mod1)
fitted <- fitted(mod1)
plot(fitted, resids)

#note: trial_number is within-block (i.e., 1-40)
minfo[["mod1.1"]] <- c(fixed="block_trial_number, block number", l2="Intercept/Subject")
mod1.1 <- lmer(rt_log ~  trial_number + block_number + (1|subject), data = data); summary(mod1)
resids <- residuals(mod1.1)
fitted <- fitted(mod1.1)
plot(fitted, resids)
dependlab::render_flex_aictab(minfo=minfo, mod0, mod1, mod1.1) %>% autofit()
```

### Adding previous RT
Also z-score trial number
```{r}
minfo[["mod2"]] <- c(fixed="block_trial_number, block number, previousRT", l2="Intercept/Subject")
mod2 <- lmer(rt_log ~ trial_z + block_number + prevRT_log + (1 |subject), data = data); summary(mod2) #big effects
qqnorm(resid(mod2))
AIC(mod2, mod1) #definitely worth adding prev_RT!

```


### Add task_phase
At first odd to see collinearity in trial_num and task phase, though makes sense because reversals happen after acquisitions. Maybe accounting for individual variation in trial number will help? 

```{r}
minfo[["mod3.1"]] <- c(fixed="block_trial_number, block number, previousRT, Task Phase", l2="Intercept, Trial_z /Subject")
mod3 <- lmer(rt_log ~ trial_z + block_number + prevRT_log + task_phase + (1 |subject), data = data); 
car::vif(mod3)
mod3.1 <- lmer(rt_log ~ trial_z + block_number + prevRT_log + task_phase + (1 + trial_z |subject), data = data); 
car::vif(mod3.1) #yes, seems to work
AIC(mod2, mod3, mod3.1) #and improves our fit but a good chunk
```

### Add Feedback (previous percieved error) and response (correct vs. incorrect current choice)
Moderate improvements and interesting effects
```{r}
minfo[["mod4"]] <- c(fixed="block_trial_number, block number, previousRT, Task Phase, Previous Feedback", l2="Intercept, Trial_z /Subject")
mod4 <- lmer(rt_log ~ trial_z + block_number + prevRT_log + task_phase + prevFeedback + (1 + trial_z |subject), data = data)
summary(mod4)
AIC(mod4, mod3)
```

### Experimentation with Random Effects

```{r}
minfo[["mod4.1"]] <- c(fixed="block_trial_number, block number, previousRT, Task Phase, Previous Feedback, Response", l2="Intercept, Trial_z /Subject")
mod4.1 <- lmer(rt_log ~ trial_z + block_number + prevRT_log + task_phase + prevFeedback + Response + (1 + trial_z |subject), data = data)
minfo[["mod4.0"]] <- c(fixed="block_trial_number, block number, previousRT, Task Phase, Previous Feedback*Response", l2="Intercept, Trial_z /Subject")
mod4.0 <- lmer(rt_log ~ trial_z + block_number + prevRT_log + task_phase + prevFeedback*Response + (1 + trial_z |subject), data = data)

dependlab::render_flex_aictab(minfo=minfo, mod0, mod1, mod1.1, mod3.1, mod4, mod4.1, mod4.2) %>% autofit()
```


### Adding Random effect of previous feedback (percieved previous error)

```{r}
minfo[["mod5"]] <- c(fixed="Total Trial, previousRT, Task Phase, Previous Feedback", l2="Intercept, Total Trial, previous Feedback /Subject")
mod5 <- lmer(rt_log ~ total_trial_z + task_phase + prevRT_log + prevFeedback + (1 + total_trial_z + prevFeedback |subject), data = data);
mod5.1 <- lmer(rt_log ~ trial_z + block_number + task_phase + prevRT_log + prevFeedback + (1 + trial_z + prevFeedback |subject), data = data);
AIC(mod4, mod5, mod5.1)
```

```{r}
minfo[["mod6"]] <- c(fixed="Total Trial, previousRT, Task Phase, PrevFeedback", l2="Intercept, Total Trial,prevFeedback previousRT /Subject")
mod6 <- lmer(rt_log ~ total_trial_z + task_phase + prevRT_log + prevFeedback + (1 + total_trial_z + prevFeedback + prevRT_log |subject), data = data);
```

```{r}
minfo[["mod7"]] <- c(fixed="Total Trial, previousRT, Task Phase, Previous Feedback", l2="Intercept, Total Trial, previousRT /Subject")
mod7 <- lmer(rt_log ~ total_trial_z + task_phase + prevRT_log + Response*prevFeedback + (1 + total_trial_z + prevRT_log |subject), data = data);
dependlab::render_flex_aictab(minfo=minfo, mod0, mod1, mod1.1, mod3.1, mod4, mod4.1,mod5,mod6, mod7) %>% autofit()
```


```{r}
minfo[["mod8"]] <- c(fixed="Total Trial, previousRT, Task Phase, Previous Feedback*Response", l2="Intercept, Total Trial, previousRT /Subject")
mod8 <- lmer(rt_log ~ total_trial_z + task_phase + prevRT_log + prevFeedback + (1 + total_trial_z + prevFeedback + prevRT_log |subject) + (1 |subject:task_phase), data = data);
car::vif(mod8)
summary(mod8)
plotREsim(REsim(mod8))
```



```{r}
minfo[["mod9"]] <- c(fixed="Total Trial, previousRT, Task Phase, Previous Feedback", l2="Intercept, Total Trial, previousRT /Subject")
mod9 <- lmer(rt_log ~ total_trial_z + task_phase + prevRT_log + prevFeedback + gen + (1 + total_trial_z + prevRT_log + prevFeedback |subject) + (1 |subject:task_phase), data = data);
summary(mod9); car::vif(mod9)
dependlab::render_flex_aictab(minfo=minfo, mod0, mod1, mod1.1, mod3.1, mod4, mod4.1,mod5,mod6, mod7, mod8, mod9) %>% autofit()

```


```{r}
minfo[["mod10"]] <- c(fixed="Total Trial, previousRT, Task Phase, Previous Feedback", l2="Intercept, Total Trial, previousRT /Subject")
mod10 <- lmer(rt_log ~ total_trial_z + task_phase + prevRT_log + prevFeedback + gen + PSWQ_Tot + PAI_AI + (1 + total_trial_z + prevRT_log + prevFeedback |subject) + (1 |subject:task_phase), data = data);
summary(mod10); car::vif(mod10)
dependlab::render_flex_aictab(minfo=minfo, mod0, mod1, mod1.1, mod3.1, mod4, mod4.1,mod5,mod6, mod7, mod8, mod9, mod10) %>% autofit()

```




