---
title: "glmers for reversal: random effects"
author: "Sophie Paolizzi"
date: "4/4/2022"
output: html_document
---

### Random_effects highlights: Key models. 

```{r setup, include=FALSE}
pacman::p_load(tidyverse, dplyr, sjPlot, readr, janitor, ggplot2,wesanderson, cowplot, flextable, plotly, emmeans, lme4, qualtRics, sjPlot, circular, pracma, cowplot, psych, lattice)
##### Load Data and setwd
ll = FALSE
if (ll == TRUE) {
  home_directory <- "/proj/mnhallqlab/users/sophie/ReversalTask/"
  data_dir <- file.path(paste0(home_directory, "data/"))
} else {
  home_directory <- "~/github_repos/ReversalTask/"
  data_dir <- file.path(paste0(home_directory, "Data/"))
}
load(file = paste0(data_dir,'base_effects_data.RData'))

data <- df %>% dplyr::filter(rt !=0) %>% dplyr::filter(!isResponseCorrect == 0) %>% filter(subject != 270470)

data$rt_log <- log(data$rt)
data$rt_inv<- -1/1000*(data$rt)
minfo<- list()
load("~/github_repos/Cannon_Task/Analysis/lmer/glmer_mods.Rdata")
data$ResponseCorrect_num <- data$ResponseCorrect_num %>% dplyr::recode("-1" = 0, "1" = 1)
data$trial_z <- scale(data$trial_number)
data$total_trial_z <- scale(data$total_trialnum)
data$prevRT_log <- lag(log(data$rt))
data$prevResponse<- relevel(as.factor(data$prevResponse), ref = "incorrect_response")
data$prevFeedback<- relevel(as.factor(data$prevFeedback), ref = "incorrect_feedback")
data$task_phase <- relevel(as.factor(data$task_phase), ref = "Acquisiton")
```

### Beginning to deal with random effects; Four-way model
Clearly not going to work... 
```{r}
minfo[["mod0"]] <- c(fixed="tot_trial_z, PrevRT, phase*prevFeed, prevFeed*prevResp", l2="Intercept + Prev_response/Subject")
mod0 <- glmer(ResponseCorrect_num ~ total_trial_z + prevRT_log + prevFeedback*task_phase + prevFeedback*prevResponse + (1  + responseAndFeedbackCategory|subject), data = data, family = binomial, control = glmerControl(optimizer = "bobyqa"))
```

### Testing feedback, phase, and response random effects
Lowest AIC appears to include task_phase, previous feedback, and previous response. 
```{r}
minfo[["mod1"]] <- c(fixed="total_trial_z, PrevRT, task phase, previous response*previous feedback", l2="Intercept + Prev_response/Subject; intercept+ prevFeedback + prevResponse/subject")
mod1 <- glmer(ResponseCorrect_num ~ total_trial_z + prevRT_log + prevFeedback*task_phase + prevFeedback*prevResponse + (1  + prevResponse + prevFeedback |subject), data = data, family = binomial, control = glmerControl(optimizer = "bobyqa"))

minfo[["mod1.1"]] <- c(fixed="total_trial_z, PrevRT, task phase, prevFeedback*task_phase, previous response*previous feedback", l2="Intercept, prevResponse, prevFeedback, task_phase/Subject")
mod1.1 <- glmer(ResponseCorrect_num ~ total_trial_z + prevRT_log + prevFeedback*task_phase + prevFeedback*prevResponse + (1  + prevResponse + prevFeedback + task_phase |subject), data = data, family = binomial, control = glmerControl(optimizer = "bobyqa"))

AIC(mod0, mod1, mod1.1)
summary(mod1.1) #noticing heavy correlation w prevResponse effect? Not sure how to handle
car::vif(mod1.1) #not bad

```

### Testing previous feedback crossed effect
does it make sense to have previous feedback crossed effect or subject|feedback as a nested effect? Seems that this doesn't do much for us and is still very correlated with the prevResponse variable...

```{r}
minfo[["mod2.0"]] <- c(fixed="total_trial_z, PrevRT, task phase, prevFeedback*task_phase, prevFeedback*prevResponse", l2="Intercept + Prev_response/subject; intercept, prevResponse /subject:task_phase")
mod2 <- glmer(ResponseCorrect_num ~ total_trial_z + prevRT_log + task_phase + prevFeedback*task_phase + prevFeedback*prevResponse + (1 + prevResponse + task_phase |subject) + (1| prevFeedback), data = data, family = binomial, control = glmerControl(optimizer = "bobyqa")) #singular fit

mod2.0 <- glmer(ResponseCorrect_num ~ total_trial_z + prevRT_log + task_phase + prevFeedback*task_phase + prevFeedback*prevResponse + (1 + prevResponse + task_phase |subject) + (1| subject:prevFeedback), data = data, family = binomial, control = glmerControl(optimizer = "bobyqa")) #not a better fit
VarCorr(mod2.0)
AIC(mod1.1, mod2, mod2.0)
car::vif(mod2)
```

### Testing previous response crossed/nested effect
Clearly, accounting for the prevresponse and prevfeedback effects in the random effects structure is working. The most parsimonious approach for now seems to be examining this at only a subject:prevResponse level. So, there is something special happened with correct vs. incorrect responses 
```{r}
mod2.01 <- glmer(ResponseCorrect_num ~ total_trial_z + prevRT_log + task_phase + prevFeedback*task_phase + prevFeedback*prevResponse + (1 + prevFeedback + task_phase |subject) + (1| prevResponse), data = data, family = binomial, control = glmerControl(optimizer = "bobyqa")) #singular

mod2.1 <- glmer(ResponseCorrect_num ~ total_trial_z + prevRT_log + task_phase + prevFeedback*task_phase + prevFeedback*prevResponse + (1 + prevFeedback + task_phase |subject) + (1| subject:prevResponse ), data = data, family = binomial, control = glmerControl(optimizer = "bobyqa")) #singular

mod2.2 <- glmer(ResponseCorrect_num ~ total_trial_z + prevRT_log + task_phase + prevFeedback*task_phase + prevFeedback*prevResponse + (1 + prevFeedback + task_phase |subject) + (1| subject:prevResponse ), data = data, family = binomial, control = glmerControl(optimizer = "bobyqa")) #singular

mod2.3 <- glmer(ResponseCorrect_num ~ total_trial_z + prevRT_log + task_phase + prevFeedback*task_phase + prevFeedback*prevResponse + (1 + prevFeedback + task_phase | subject/prevResponse), data = data, family = binomial, control = glmerControl(optimizer = "bobyqa")) #singular


mod2.31 <- glmer(ResponseCorrect_num ~ total_trial_z + prevRT_log + task_phase + prevFeedback*task_phase + prevFeedback*prevResponse + (0 + prevFeedback + task_phase| subject/prevResponse), data = data, family = binomial, control = glmerControl(optimizer = "bobyqa")) #singular

mod2.4 <- glmer(ResponseCorrect_num ~ total_trial_z + prevRT_log + task_phase + prevFeedback*task_phase + prevFeedback*prevResponse + (1 + prevFeedback + task_phase |subject:prevResponse), data = data, family = binomial, control = glmerControl(optimizer = "bobyqa")) #NOT singular!

AIC(mod1, mod2, mod2.0, mod2.1, mod2.2, mod2.3, mod2.31, mod2.4)
car::vif(mod2.4) #looks good
VarCorr(mod2.4) # fine here too
summary(mod2.4)

minfo[["mod2.4"]] <- c(fixed="total_trial_z, PrevRT, task phase, prevFeedback*task_phase, prevFeedback*prevResponse", l2="Intercept, prevFeedback/subject:prevResponse)")
```

#### Playing with task phase
There appears to be some variance that task phase accounts for, and this seems best captured by a within-subject random slope, rather than a nested effect? Seems weird.

```{r}
#first tried, best fitting in the end, tolerate singularity? 
mod3 <- glmer(ResponseCorrect_num ~ total_trial_z + prevRT_log + task_phase + prevFeedback*task_phase + prevFeedback*prevResponse + (1 + task_phase |subject) + (1 + prevFeedback| subject:prevResponse), data = data, family = binomial, control = glmerControl(optimizer = "bobyqa")) #singular

#singular, not super helpful/additive
mod3.0 <- glmer(ResponseCorrect_num ~ total_trial_z + prevRT_log + task_phase + prevFeedback*task_phase + prevFeedback*prevResponse + (1 |task_phase) + (1 + prevFeedback| subject:prevResponse), data = data, family = binomial, control = glmerControl(optimizer = "bobyqa")) #singular

#how does this do?
mod3.0 <- glmer(ResponseCorrect_num ~ total_trial_z + prevRT_log + task_phase + prevFeedback*task_phase + prevFeedback*prevResponse + (1 + prevFeedback*prevResponse | subject:task_phase), data = data, family = binomial, control = glmerControl(optimizer = "bobyqa")) #singular

#this seems to be the same effect
mod3.01 <- glmer(ResponseCorrect_num ~ total_trial_z + prevRT_log + task_phase + prevFeedback*task_phase + prevFeedback*prevResponse + (1 ) + (1 + prevFeedback+prevResponse), data = data, family = binomial, control = glmerControl(optimizer = "bobyqa")) #singular

minfo[["mod3"]] <- c(fixed="total_trial_z, PrevRT, task phase,  prevFeedback*task_phase, prevFeedback*prevRespons", l2="Intercept, task phase/subject; Intercept,prevFeedback/subject:prevResponse")

```

```{r, run = FALSE}
#same as above
mod3.01 <- glmer(ResponseCorrect_num ~ total_trial_z + prevRT_log + task_phase + prevFeedback*task_phase + prevFeedback*prevResponse + (0 + task_phase |subject) + (0 + prevFeedback| subject:prevResponse), data = data, family = binomial, control = glmerControl(optimizer = "bobyqa")) #singular

mod3.1 <- glmer(ResponseCorrect_num ~ total_trial_z + prevRT_log + task_phase + prevFeedback*task_phase + prevFeedback*prevResponse + (1 |subject) + (1 + prevFeedback + task_phase| subject:prevResponse), data = data, family = binomial, control = glmerControl(optimizer = "bobyqa")) #singular

#maybe a crossed effect? - asingular, don't use
mod3.2 <- glmer(ResponseCorrect_num ~ total_trial_z + prevRT_log + task_phase + prevFeedback*task_phase + prevFeedback*prevResponse + (1 |task_phase) + (0 + prevFeedback | subject:prevResponse), data = data, family = binomial, control = glmerControl(optimizer = "bobyqa")) 
dependlab::check_singularity(mod3.01)

mod3.3 <- glmer(ResponseCorrect_num ~ total_trial_z + prevRT_log + task_phase + prevFeedback*task_phase + prevFeedback*prevResponse + (1 |subject:task_phase) + (0 + prevFeedback | subject:prevResponse), data = data, family = binomial, control = glmerControl(optimizer = "bobyqa"))
dependlab::check_singularity(mod3.01) #not singular

mod3.4 <- glmer(ResponseCorrect_num ~ total_trial_z + prevRT_log + task_phase + prevFeedback*task_phase + prevFeedback*prevResponse + (1 + prevFeedback + task_phase| subject:prevResponse), data = data, family = binomial, control = glmerControl(optimizer = "bobyqa"))

AIC(mod2.4, mod3, mod3.4, mod3.3)
VarCorr(mod3.0) #singular task_phase
VarCorr(mod2.4) #way better correlation structure - maybe worth carrying forward
```

#### prevRT random effect
is this worth considering? seems singular...
```{r}
minfo[["mod4"]] <- c(fixed="total_trial_z, PrevRT, task phase,  prevFeedback*task_phase, prevFeedback*prevResponse", l2="Intercept, Prev_response/Subject; intercept,prevResponse/subject:task_phase")
mod4 <- glmer(ResponseCorrect_num ~ total_trial_z + prevRT_log + task_phase + prevFeedback*task_phase + prevFeedback*prevResponse + (1 + prevRT_log |subject) + (1 + prevFeedback + task_phase |subject:prevResponse), data = data, family = binomial, control = glmerControl(optimizer = "bobyqa"))
dependlab::check_singularity(mod4)
AIC(mod3,mod4)
```

### trial random effects
It seems this is also singular - might be getting to the end of our usefulness here.
```{r}
minfo[["mod5"]] <- c(fixed="total_trial_z, PrevRT, task phase,  prevFeedback*task_phase, prevFeedback*prevResponse", l2="Intercept, Prev_response/Subject; intercept,prevResponse/subject:task_phase")
mod5 <- glmer(ResponseCorrect_num ~ total_trial_z + prevRT_log + task_phase + prevFeedback*task_phase + prevFeedback*prevResponse + (1 + task_phase + total_trial_z |subject) + (1 + prevFeedback| subject:prevResponse), data = data, family = binomial, control = glmerControl(optimizer = "bobyqa"))
dependlab::check_singularity(mod5)
AIC(mod2.4, mod5)
```
#Check on age and sex effects before sending to ranef/individual differences. 
Like in the cannon data, seems gen does the most work here. 
```{r}
data$age_scaled <- scale(data$age)
#just trying to see if we can get away with 3-way interaction once other things are accounted for
mod6 <- glmer(ResponseCorrect_num ~ total_trial_z + prevRT_log + task_phase + prevFeedback*task_phase + prevFeedback*prevResponse + age_scaled + gen + (1 + prevFeedback + task_phase| subject:prevResponse), data = data, family = binomial, control = glmerControl(optimizer = "bobyqa")) #big ass eigenvalue
car::vif(mod6)

#
mod6.1 <- glmer(ResponseCorrect_num ~ total_trial_z + prevRT_log + task_phase + + prevFeedback*task_phase + prevFeedback*prevResponse + gen + (1 + prevFeedback + task_phase| subject:prevResponse), data = data, family = binomial, control = glmerControl(optimizer = "bobyqa"))
dependlab::check_singularity(mod6)

mod6.2 <- glmer(ResponseCorrect_num ~ total_trial_z + prevRT_log + task_phase + + prevFeedback*task_phase + prevFeedback*prevResponse + age + (1+ prevFeedback + task_phase| subject:prevResponse), data = data, family = binomial, control = glmerControl(optimizer = "bobyqa"))

AIC(mod6, mod6.1, mod6.2)
minfo[["mod6"]] <- c(fixed="total_trial_z, PrevRT, task phase,  prevFeedback*task_phase, prevFeedback*prevResponse", l2="Intercept, Prev_response/Subject; intercept,prevResponse/subject:task_phase")
dependlab::render_flex_aictab(minfo=minfo,mod0, mod1,mod2, mod2.1, mod2.4, mod3, mod3.0, mod4, mod5,mod6) %>% autofit()
VarCorr(mod6.1)
car::vif(mod6.1)
beepr::beep()
```

#can we handle the 3-way interaction?
No, we cannot. 
```{r}
mod7 <- glmer(ResponseCorrect_num ~ total_trial_z + prevRT_log + task_phase + prevFeedback*task_phase*prevResponse + gen + (1 + prevFeedback + task_phase| subject:prevResponse), data = data, family = binomial, control = glmerControl(optimizer = "bobyqa"))
dependlab::check_singularity(mod7)
VarCorr(mod7)
car::vif(mod7)
#beepr::beep()
```


```{r}
mod_matrix <- as.tibble(ranef(mod6.1), names= "term") %>% separate(grp, into = c("subject", "response"))
coefficients <- mod_matrix %>% pivot_wider(
  names_from = c(term, response),
  values_from = c(condsd, condval))

coefficients

 with_coefs <- left_join(coefficients, data, by = 
            "subject")
             
save(with_coefs, file = "~/github_repos/ReversalTask/Data/df_with_coefficients.RData")
```

